**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2018-03-12 doc/adaAbstract.Rmd
updated variable names

knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

@@

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_poster("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  scatter_plot_poster("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  cor.test(formula = ~ ACR + udbpCrRatio, data = ., method = "spearman")
```

@@

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  scatter_plot_poster("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine")

@@

ds %>% 
  filter(!(acr_status == "Macroalbuminuria")) %>% 
  cor.test(formula = ~ eGFR + udbpCrRatio, data = ., method = "spearman")
```

>>>>

knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

@@

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_poster("acrStatus", "log(udbpCr)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  scatter_plot_poster("log(ACR)", "log(udbpCr)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  cor.test(formula = ~ ACR + udbpCr, data = ., method = "spearman")
```

@@

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  scatter_plot_poster("eGFR", "log(udbpCr)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine")

@@

ds %>% 
  filter(!(acrStatus == "Macroalbuminuria")) %>% 
  cor.test(formula = ~ eGFR + udbpCr, data = ., method = "spearman")
```
